SDM\_the\_search\_for\_powers\_of\_2\_everywhere

### 2018-05-03 Chapters/Chapter01.tex
Hathor governance and other minor changes.

Bitcoin is a computer network in which nodes act like clerks performing clearing. A transaction clearing consists of ensuring that the transaction is settled according to the rules. In order to do that, every node stores a copy of Bitcoin's ledger, which records both all transactions and users' balance. When new transactions are added to the ledger, the balances are updated. It is said that Bitcoin is distributed because its ledger is public and is stored in thousands of computers. Even though the ledger is public, balances are anonymous and no one knows who owns which funds. If an attacker tries to change anything, the remaining of the network is able to detect it and ignore the change.

@@

Bitcoin provides interesting incentives to all players, users and miners. On the one hand, users may have incentives to use Bitcoin because (i) the fees are small and does not depend on the amount being transfered --- but only in the size (in bytes) of the transaction ---; (ii) the transfers will be confirmed in a well-known period; (iii) it is not possible to revert an already confirmed transfer, not even with a judicial order; and (iv) and the currency issuance rate is well-known and preset in Bitcoin's rules, which makes Bitcoin's supply predictable and trustworthy, different from fiat currencies which depends on decisions of their central banks --- i.e., it would be virtually impossible to face a hyper inflation in Bitcoin due to currency issuance. On the other hand, miners have incentive to mine Bitcoin because new Bitcoins are found every ten minutes, and they may also collect the fees of unconfirmed transactions. It is important to highlight that anyone can become a miner, and there is no entry cost besides the mining equipment. These incentives have kept the Bitcoin network up and running since 2009 with barely any interruptions (99.99\% uptime). For further information about incentives, see \citet{ma2018market, catalini2016some}.

@@

Generating new transactions in Bitcoin has a tiny computational cost because one only has to generate the transaction itself, digitally sign it, and propagate it in the Bitcoin network. On the one hand, it means that any device is capable of generating new transactions, but, on the other hand, it makes Bitcoin susceptible to spam attacks. One may generate hundreds of thousands of new valid transactions, overloading the unconfirmed transactions pool and saturating the network. This spam problem has happened several times and affects Bitcoin's trustworthy. \citet{bitcoinspam2017} reports a possible spam attack lasting at least 18 months.

@@

Iota uses a DAG model, called tangle, which has a different design than Bitcoin's blockchain. It has neither mining nor confirmation blocks and transaction fees. Each transaction has its own proof-of-work and is used to confirm other transactions, forming a directed acyclic graph of transactions. Thus, a transaction is said to be confirmed when there is enough proof-of-work from the transactions confirming it directly or indirectly. There is no other way to confirm transactions but generating new transactions.

@@

Next, we will do a mathematical analysis of Bitcoin in order to better understand its minings properties, how a fork would affect the network and its security against attackers.

>>>>

Bitcoin is a computer network in which nodes act like clerks performing clearing. A transaction clearing consists of ensuring that the transaction is settled according to the rules. In order to do that, every node stores a copy of Bitcoin's ledger, which records both all transactions and users' balance. When new transactions are added to the ledger, the balances are updated. It is said that Bitcoin is distributed because its ledger is public and is stored in thousands of computers. Even though the ledger is public, balances are anonymous and no one knows who owns which funds\footnote{There are some techniques which may de-anonymize transactions in specific situations, even when users are using Tor network. For further information, see \citet{shentu2015research, biryukov2014deanonymisation, jawaheri2018small}.}. If an attacker tries to change anything, the remaining of the network is able to detect it and ignore the change.

@@

% TODO After the year of 2140, there will be only fees to be collected.
Bitcoin provides interesting incentives to all players, users and miners. On the one hand, users may have incentives to use Bitcoin because (i) the fees are small and does not depend on the amount being transfered --- but only in the size (in bytes) of the transaction ---; (ii) the transfers will be confirmed in a well-known period; (iii) it is not possible to revert an already confirmed transfer, not even with a judicial order; and (iv) and the currency issuance rate is well-known and preset in Bitcoin's rules, which makes Bitcoin's supply predictable and trustworthy, different from fiat currencies which depends on decisions of their central banks --- i.e., it would be virtually impossible to face a hyper inflation in Bitcoin due to currency issuance. On the other hand, miners have incentive to mine Bitcoin because new Bitcoins are found every ten minutes, and they may also collect the fees of unconfirmed transactions. It is important to highlight that anyone can become a miner, and there is no entry cost besides the mining equipment. These incentives have kept the Bitcoin network up and running since 2009 with barely any interruptions (99.99\% uptime). For further information about incentives, see \citet{ma2018market, catalini2016some}.

@@

Generating new transactions in Bitcoin has a tiny computational cost because one only has to generate the transaction itself, digitally sign it, and propagate it in the Bitcoin network. On the one hand, it means that any device is capable of generating new transactions, but, on the other hand, it makes Bitcoin susceptible to spam attacks. One may generate hundreds of thousands of new valid transactions, overloading the unconfirmed transactions pool and saturating the network. This spam problem has happened several times and affects Bitcoin's trustworthy. \citet{bitcoinspam2017} reports a possible spam attack lasting at least contiguous 18 months.

@@

Iota uses a DAG model, called tangle, which has a different design than Bitcoin's blockchain. It has neither mining nor confirmation blocks and transaction fees. Each transaction has its own proof-of-work\footnote{The mechanism that assures the immutability is the proof-of-work, which makes it computationally infeasible to tamper with transactions. It will be explained later in details.} and is used to confirm other transactions, forming a directed acyclic graph of transactions. Thus, a transaction is said to be confirmed when there is enough proof-of-work from the transactions confirming it directly or indirectly. There is no other way to confirm transactions but generating new transactions.

@@

Next, I will do a mathematical analysis of Bitcoin in order to better understand its minings properties, how a fork would affect the network and its security against attackers. It is not necessary to do a mathematical analysis of Iota, because it has already been done in \citet{tangle2016}.

### 2018-05-03 Chapters/hathor-architecture.tex
Hathor governance and other minor changes.

- Punishment for miners/transactions which does not comply with the rules.

- Rule change policy.

>>>>

In general, cryptocurrencies are decentralized, which means there is no central authority who decides its future, i.e., no one can enforce their will. Every decision must be accepted by its community, which means the community must agree. But what happens if they do not agree? When a consensus is not reached, the rules remain the same and the cryptocurrency may stall. The lack of a central authority may generate long debates, split the community, slow down strategic decision-making, and, ultimately, come to a ``civil war''---it is precisely what happened between Bitcoin Core (BTC) and Bitcoin Cash (BCH) in 2017 \citep{bloomberg2017civilwar, forbes2017civilwar}.

Governance is an important part of a cryptocurrency because it must evolve, which means its community must agree into changing the rules. Governance is an agreement of how the community will proceed to change the rules.

Despite the large literature available about governance, what separates Blockchain-based cryptocurrencies from them is the decentralization (against the hierarchical model). The number of papers about governance in decentralized cryptocurrencies has been growing, but it still lacks a solution. \citet{hacker2017corporate} resorts to the theory of complex systems and proposes a governance framework for decentralized cryptocurrencies, which is, in summary, a centralized coordination entity. \citet{hsieh2017internal} has analyzed the effects of governance in returns using panel data on several cryptocurrencies. They present a deeper discussion about the parts of a governance mechanism and concludes that

\begin{quote}
``... on the one hand, investors value cryptocurrencies’ core value proposition, rooted in decentralization; but on the other hand, are suspicious of decentralized governance at higher levels in the organization because they could slow down strategic decision-making (e.g., regarding the introduction of new innovations) or create information asymmetries between investors and technologists.''
\end{quote}

I believe that the solution to a good governance will come from financial incentives to all players to find a common ground. In Bitcoin, users have less bargaining power than miners because they do not contribute with work, whereas, in Hathor, both miners and users are working together. So, when it comes to changing the rules, the bargaining power is more distributed than in Bitcoin. The distribution depends on the ratio of the miners' hashpower and the users' hashpower. The higher the ratio, the closer to Bitcoin's governance. The lower the ratio, the higher the bargaining power of the users.

%- Punishment for miners/transactions which does not comply with the rules.
%- Rule change policy.
